Type Refinements for the Working Class

### 2016-01-01 paper.tex
remove independed nominal possibility section (#13)

Another comonadic refinement modality is \emph{nominal necessity}
$\HypJ{\Refines{\Upsilon}{\square\phi}{\tau}}{\Refines{\Upsilon}{\phi}{\tau}}$,
which expresses the independence of an object from \emph{any} atoms at all. For
any renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}%
, we define nominal necessity as follows:
\[
  \infer={
    \RMemEq{\Upsilon'}{M}{N}{\square\phi}
  }{
    \exists\Member{L}{\Exprs_\tau(\cdot)}.
    \begin{array}{l}
      \RMemEq{\Upsilon'}{L}{M}{\phi}\\
      \RMemEq{\Upsilon'}{L}{N}{\phi}
    \end{array}
  }
\]

@@

%% \subsubsection{Nominal Possibility}
%%
\section{Related Work}

>>>>

Another comonadic refinement modality is \emph{nominal necessity}
$\HypJ{\Refines{\Upsilon}{\Box\phi}{\tau}}{\Refines{\Upsilon}{\phi}{\tau}}$,
which expresses the independence of an object from \emph{any} atoms at all. For
any renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}%
, we define nominal necessity as follows:
\[
  \infer={
    \RMemEq{\Upsilon'}{M}{N}{\Box\phi}
  }{
    \exists\Member{L}{\Exprs_\tau(\cdot)}.
    \begin{array}{l}
      \RMemEq{\Upsilon'}{L}{M}{\phi}\\
      \RMemEq{\Upsilon'}{L}{N}{\phi}
    \end{array}
  }
\]

@@

\section{Related Work}
